Safe Memory Regions for Big Data Processing

### 2016-06-03 paper/type-inference.tex
typeinference

\textbf{TO DO:}
\begin{itemize}
\item Add destructive object-field-update \emph{x.f := y} to the language.
\item Add if-then-else to the language.
\item Note that the claim that all region variables will be unified with some concrete
region fails in the case of a method that recursively calls itself (and, hence, does not
terminate). In this case, the region variables in the return type are not constrained.
Similarly for non-terminating mutual recursion. These are uninteresting (in essence, the
return type can be taken to be unit instead).
\item Discuss the safety of virtual method invocation, which provides a limited form
of existentially quantifying regions and instantiating (unpacking) them because a
derived class may have more region parameters than a base class.
\item Discuss the subtyping rule used to check an overriding method (in the static
semantics).
\item Mention that constraints are in the theory of partial orders?
\end{itemize}

@@

Elaborating $\absof{\FB}$ expressions to $\FB$ expressions involves
(a). replacing core types in variable declarations and \C{new}
expressions with fresh region type templates, and (b). explicitly
instantiating region parameters of methods with fresh region variables
in method calls and function applications. This elaboration is
performed with respect to the polymorphic type templates of classes
and methods computed as per \S\ref{sec:fb-templatization}.

@@

>>>>

\textbf{TO DO:}
\begin{itemize}
\item Add destructive object-field-update \emph{x.f := y} to the language.
\item Add if-then-else to the language.
\item Omit constructors from classes (and use an implicit constructor).
\item Note that the claim that all region variables will be unified with some concrete
region fails in the case of a method that recursively calls itself (and, hence, does not
terminate). In this case, the region variables in the return type are not constrained.
Similarly for non-terminating mutual recursion. These are uninteresting (in essence, the
return type can be taken to be unit instead).
\item Discuss the safety of virtual method invocation, which provides a limited form
of existentially quantifying regions and instantiating (unpacking) them because a
derived class may have more region parameters than a base class.
\item Discuss the subtyping rule used to check an overriding method (in the static
semantics).
\item Mention that constraints are in the theory of partial orders?
\end{itemize}

@@

@@

%Elaborating $\absof{\FB}$ expressions to $\FB$ expressions involves
%(a). replacing core types in variable declarations and \C{new}
%expressions with fresh region type templates, and (b). explicitly
%instantiating region parameters of methods with fresh region variables
%in method calls and function applications. This elaboration is
%performed with respect to the polymorphic type templates of classes
%and methods computed as per \S\ref{sec:fb-templatization}.
